---
title: "Cake Analysis - Dirty Data Project"
author: "Stuart McColl"
date: "09/11/2020"
output: 
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Analysis Questions

1. Which cake has the most cocoa in it?
2. For sponge cake, how many cups of ingredients are used in total?
3. How many ingredients are measured in teaspoons?
4. Which cake has the most unique ingredients?
5. Which ingredients are used only once?

### Step One
Load Libraries

```{r, warning=FALSE, message=FALSE}

library(tidyverse)
library(here)

```

### Step Two
Read in Cleaned Data

```{r, warning=FALSE, message=FALSE}

cake_clean_data <- read_csv("/Users/Natifu/dirty_data_stu/task_2_cake/clean_data/cake_clean.csv")


```


### Question One
Which cake has the most cocoa in it?

```{r}

cake_cocoa <- cake_clean_data %>%
  filter(ingredient == "Cocoa") %>%
  arrange(desc(ingredient))

```


### Question Two
For sponge cake, how many cups of ingredients are used in total?


```{r}

cake_clean_data %>%
  filter(cake == "Sponge", measure == "cup") %>%
  summarise(sum_of_cups = sum(measurement))


```

### Question Three
How many ingredients are measured in teaspoons?

```{r}

cake_teaspoon <- cake_clean_data %>%
  filter(measure == "teaspoon") %>%
  group_by(ingredient, measure) %>%
  summarise(teaspoon_count = n()) %>%
  arrange(desc(teaspoon_count))

nrow(cake_teaspoon)



```













