---
title: "bb_candy_analysis_stu"
author: "Stuart McColl"
date: "12/11/2020"
output: 
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Analysis Questions

1. What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

2. What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?

3. For each of joy, despair and meh, which candy bar revived the most of these ratings?

4. How many people rated Starburst as despair?

5. Count despair as -1, joy as +1 and meh as 0.

6. What was the most popular candy bar by this rating system for each gender in the dataset?

7. What was the most popular candy bar in each year?

8. What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?


### Step One
Load Libraries

```{r, warning=FALSE, message=FALSE}

library(tidyverse)

```

### Step Two
Read in Cleaned Data

```{r, warning=FALSE, message=FALSE}

bb_candy_clean <- read_csv("/Users/Natifu/dirty_data_stu/task_4_halloween/clean_data/bb_candy_all_cleaned")

```


### Question 1

#### What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

##### For this question I simply summarised the number of ratings. There was no missing values because I dropped them during the cleaning stage:

```{r, warning=FALSE}

bb_candy_clean %>%
  summarise(number_of_ratings = n())

```
##### Answer = 769,509 ratings given.

### Question 2

#### What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?

##### For this question, I looked at the two categories separately. I applied a filter for 'TRUE' and 'FALSE', dropping any missing values and calculated the mean age, which I then rounded to a whole number:

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(trick_or_treat == TRUE) %>%
  drop_na() %>%
  summarise(average_age_who_do_trick_or_treat = round(mean(age)))

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(trick_or_treat == FALSE) %>%
  drop_na() %>%
  summarise(average_age_who_do_not_trick_or_treat = round(mean(age)))

```

##### Answer - The average age for someone who goes trick or treating is 34 and the average age for someone who does does go trick or treating is 38.

### Question 3

#### For each of joy, despair and meh, which candy bar revived the most of these ratings?

##### For this question I applied a filter for each respective rating and counted the number of ratings:

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(reaction == "joy") %>%
  group_by(item_gifted) %>%
  summarise(joy_count = n()) %>%
  arrange(desc(joy_count)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(reaction == "meh") %>%
  group_by(item_gifted) %>%
  summarise(meh_count = n()) %>%
  arrange(desc(meh_count)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(reaction == "despair") %>%
  group_by(item_gifted) %>%
  summarise(despair_count = n()) %>%
  arrange(desc(despair_count)) %>%
  slice(1)

```

##### Answer - 'Any Full Sized Candy Bar' receieved the highest 'joy' rating, 'Regular M&M's' receieved the highest 'meh' rating and 'Broken Glow Stick' recieved the highest 'despair' rating.

### Question 4

#### How many people rated Starburst as despair?

#### For this question I filtered by 'despair' and 'starburst' respectively, then applied a count:

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(reaction == "despair",
         item_gifted == "starburst") %>%
  summarise(starburst_despair_count = n())

```

#### Answer - 1,990 people rated 'starburst' as 'despair.

### Question 5

#### Count despair as -1, joy as +1 and meh as 0.

#### For this question, I recoded the reaction column and added a new column for the results:

```{r, warning=FALSE}

bb_candy_clean %>%
  mutate(reaction_code = recode(
    reaction, "despair" = -1,
              "joy" = 1,
              "meh" = 0
    ))

```

### Question 6

#### What was the most popular candy bar by this rating system for each gender in the dataset?

##### For this question, I filtered each respective gender separately and applied a count to the 'item_gifted' column:

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(gender == "male") %>%
  group_by(item_gifted) %>%
  summarise(rating_male = n()) %>%
  arrange(desc(rating_male)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(gender == "female") %>%
  group_by(item_gifted) %>%
  summarise(rating_female = n()) %>%
  arrange(desc(rating_female)) %>%
  slice(1)


```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(gender == "other") %>%
  group_by(item_gifted) %>%
  summarise(rating_other = n()) %>%
  arrange(desc(rating_other)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(gender == "undisclosed") %>%
  group_by(item_gifted) %>%
  summarise(rating_undisclosed_gender = n()) %>%
  arrange(desc(rating_undisclosed_gender)) %>%
  slice(1)

```

#### Answer - The top rated candy for male, femal and other is 'Regular M&M's and the top rated candy for any gender 'undisclosed' was 'Reese's Peanut Butter Cups.

### Question 7

#### What was the most popular candy bar in each year?

#### For this question, I applied a filter to the 'year' column and applied a count:

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(date >= "2015-01-01" & date <= "2015-12-31") %>%
  group_by(item_gifted) %>%
  summarise(rating_score_2015 = n()) %>%
  arrange(desc(rating_score_2015)) %>%
  slice(1)
  
```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(date >= "2016-01-01" & date <= "2016-12-31") %>%
  group_by(item_gifted) %>%
  summarise(rating_score_2016 = n()) %>%
  arrange(desc(rating_score_2016)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(date >= "2017-01-01" & date <= "2017-12-31") %>%
  group_by(item_gifted) %>%
  summarise(rating_score_2017 = n()) %>%
  arrange(desc(rating_score_2017)) %>%
  slice(1)

```

#### Answer - The top rated candy for 2015 was 'Reese's Peanut Butter Cups', for 2016 it was 'Any Full Sized Candy Bar' and for 2017, unfortunately I was unable to get a result as it looks like the rows for 2017 did not 'bind' during the cleaning stage.

### Question 8

#### What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?

##### For this question, the first thing I did was pull out the 'unique' names for the country column. I then applied a filter for each country, grouped it by the 'item_gifted' and applied a count: 

```{r, warning=FALSE}

unique(bb_candy_clean$country)

```


```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "undisclosed") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_undisclosed_country = n()) %>%
  arrange(desc(top_candy_undisclosed_country)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "canada") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_canada = n()) %>%
  arrange(desc(top_candy_canada)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "united states") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_united_states = n()) %>%
  arrange(desc(top_candy_united_states)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "europe") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_europe = n()) %>%
  arrange(desc(top_candy_europe)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "asia") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_asia = n()) %>%
  arrange(desc(top_candy_asia)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "central america") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_central_america = n()) %>%
  arrange(desc(top_candy_central_america)) %>%
  slice(1)

```

```{r, warning=FALSE}
bb_candy_clean %>%
  filter(country == "new zealand") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_new_zealand = n()) %>%
  arrange(desc(top_candy_new_zealand)) %>%
  slice(1)


```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "north america") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_north_america = n()) %>%
  arrange(desc(top_candy_north_america)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "south america") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_south_america = n()) %>%
  arrange(desc(top_candy_south_america)) %>%
  slice(1)

```

```{r, warning=FALSE}

bb_candy_clean %>%
  filter(country == "africa") %>%
  group_by(item_gifted) %>%
  summarise(top_candy_africa = n()) %>%
  arrange(desc(top_candy_africa)) %>%
  slice(1)

```

##### Answer:

* Canada - M&M's Regular
* Europe - M&M's Regular
* Asia - M&M's Regular
* Central America - Anonymous Brown Globs
* New Zealand - Any Full Sized Candy Bar
* North America - M&M's Regular
* South America - 100 Grand Bar
* Africa - 100 Grand Bar

### End








