---
title: "bb_candy_analysis_stu"
author: "Stuart McColl"
date: "12/11/2020"
output: 
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Analysis Questions

1. What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

2. What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?

3. For each of joy, despair and meh, which candy bar revived the most of these ratings?

4. How many people rated Starburst as despair?


### Step One
Load Libraries

```{r, warning=FALSE, message=FALSE}

library(tidyverse)

```

### Step Two
Read in Cleaned Data

```{r, warning=FALSE, message=FALSE}

bb_candy_clean <- read_csv("/Users/Natifu/dirty_data_stu/task_4_halloween/clean_data/bb_candy_all_cleaned")

```


### Question 1

##### What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

```{r}

bb_candy_clean %>%
  summarise(number_of_ratings = n())

```

### Question 2

What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?

```{r}



```




